### 2018-07-10 latex/discussion.tex
edited new discussion

A detailed analysis of sequence variances in NamPRT revealed that only Deuterostomia that have NNMT but not NADA, have a sequence insertion in the N-terminal part of NamPRT that according to our experimental analysis seems to enable the high affinity of the enzyme. This in turn would suggest that also the bacterial enzymes doe not have a high substrate affinity, a finding that could potentially be exploited for antibiotics development.

We completely neglected the potential effects of cosubstrates of the pathway investigated such as the presence of targets of the NAD-consuming enzymes, such as acetylated proteins for sirtuins for example, or the requirement of PRPP\todo{insert full name and but PRPP in brackets} and ATP that are rrequired for NMN synthesis by NamPRT  or the presence of methyl donor \textit{S}-adenosyl methionine (SAM) and its precursor methionine that have been shown to potentially limit the effect of NNMT\cite{PMID:23455543 }. These should be included in future analysis. The challenge is, however, that currently information about the in vivo concentration of those co-substrates are very limited. We assume that this will improve in the future as new, more sensitive, methods for metabolite measurements are currently developed.

@@

\subsection{Points to discuss}

+ NADA disappears but rest of pathway stays. Why?

-- NADS needed for \textit{de~novo} pathway

-- NMNAT also needed in NamPRT and \textit{de~novo} pathway

---- Is the \textit{de~novo} pathway still necessary? If we take up enough Vit B3 with the diet, why \textit{de~novo}?

-- NAPRT needed for NA that is taken up with the diet (and if NA is processed, the other two enzymes are also needed to continue processing)

>>>>

A detailed analysis of sequence variances in NamPRT revealed that only Deuterostomia that have NNMT but not NADA, have a sequence insertion in the N-terminal part of NamPRT that according to our experimental analysis seems to enable the high affinity of the enzyme. This in turn would suggest that also the bacterial enzymes doe not have a high substrate affinity and although the one bacterial NamPRT has been proven to be enzymatically active, the affinity of a bacterial enzyme has not been measured so far. The differences in activity and affinity, implying differences in substrate binding could potentially be exploited for the development of  antibiotics. But further analysis as well as potentially the crystallisation of a bacterial enzyme would be required, to see whether this could be a  approach.

In our analysis, we so far completely neglected the potential effects of cosubstrates of the pathway investigated such as the presence of targets of the NAD-consuming enzymes, such as acetylated proteins for sirtuins for example, or the requirement of PRPP\todo{insert full name and but PRPP in brackets} and ATP that are rrequired for NMN synthesis by NamPRT  or the presence of methyl donor \textit{S}-adenosyl methionine (SAM) and its precursor methionine that have been shown to potentially limit the effect of NNMT\cite{PMID:23455543 }. These should be included in future analysis. The challenge is, however, that currently information about the in vivo concentration of those co-substrates are very limited. We assume that this will improve in the future as new, more sensitive, methods for metabolite measurements are currently developed.

@@
